---
title: "Animated Map of PM2.5 concentrations in India"
author: "M. Salmon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The goal of this vignette is to show how to use the gganimate package (see <https://github.com/dgrtwo/gganimate>) for making an animated map of air PM2.5 concentrations in India. Obviously this could be adapted to other subsets of OpenAQ data.

```{r, warning=FALSE, message=FALSE}
library("ggmap")
library("ggplot2")
library("Ropenaq")
library("dplyr")
```


# First, get the data and calculate daily average

We only query locations for which we have geographical information and we only want positive concentrations. Since there are many measurements we need to loop over several pages.

```{r, warning=FALSE, message=FALSE, eval=FALSE}
measurementsIndia <- NULL
for (page in 1:7){
  print(page)
  measurementsIndia <- rbind(measurementsIndia,
                             aq_measurements(country = "IN", 
                                             has_geo = TRUE, 
                                             page = page,
                                             parameter = "pm25", 
                                             limit = 1000,
                                             date_from = "2015-09-01",
                                             value_from = 0))}
```

```{r, warning=FALSE, message=FALSE, eval=FALSE, echo=FALSE}
save(measurementsIndia, file="data/measurementsIndia.RData")
```


```{r, warning=FALSE, message=FALSE, eval=TRUE, echo=FALSE}
load("data/measurementsIndia.RData")
```

# Calculate daily averages

```{r}
dailyIndia <- measurementsIndia %>%
  group_by(day = as.Date(dateLocal),
           location) %>%
  summarize(value = mean(value)) %>%
  mutate(location = as.factor(location))
```

# Re-add longitude and latitude

```{r}
tableGeo <- unique(select(measurementsIndia, location,
                          longitude, latitude))

dailyIndia <- dailyIndia %>% left_join(tableGeo)
```

# Open map for India
```{r}
indiaMap <- get_map(location = c(65,
                                 6,
                                 97,
                                 36))
ggmap(indiaMap)
```

# Do the animated map

You'll need to have installed both gganimate (see <https://github.com/dgrtwo/gganimate>) and animation package (from CRAN), and also have the ffmpeg software (<https://www.ffmpeg.org/>)

You'll find the resulting video in the vignettes folder.

```{r, echo = TRUE, eval = FALSE}
library("gganimate")
library("animation")
minConc <- min(dailyIndia$value)
maxConc <- max(dailyIndia$value)
plotMap <- ggmap(indiaMap)+ theme_bw()+
  geom_point(data = dailyIndia, aes(x=longitude,
                                  y=latitude,
                                  frame=day,
                                       colour = value),
             size=8)+
  scale_colour_gradient(limits=c(minConc, maxConc), 
                        low="yellow", 
                        high="red") +
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        text = element_text(size=20),
        axis.title.y=element_blank(),
        panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),plot.background=element_blank())+
  ggtitle("PM 2.5 concentration") +
  theme(plot.title = element_text(lineheight=1, face="bold"))

ani.options(interval = 0.5, ani.width = 800, ani.height = 800)
gg_animate(plotMap, "map.mp4")
```
